Analysis

### 2020-02-26 reports/DRM_exp/analysis_DRM_exp1.Rmd
correlation with lower layers

df2 <- readRDS(here("data/exp_DRM1/results_with_tgtdistances_fc7_200219.rds"))
```

@@

df2 %>% 
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct),
            dist_to_proto = mean(dist_to_proto)) %>% 
  ggplot(aes(x=dist_to_proto,y=correct, col = type)) + 
  geom_point()
```

>>>>

df2 <- readRDS(here("data/exp_DRM1/results_with_tgtdistances_fc7_200219.rds"))
df2_conv5 <- readRDS(here("data/exp_DRM1/results_with_tgtdistances_conv5_200219.rds"))
```

@@

df2 %>% 
  group_by(subject_id, type) %>% 
  summarize(correct = mean(correct),
            dist_to_proto = mean(dist_to_proto)) %>% 
  ggplot(aes(x=dist_to_proto,y=correct, col = type)) + 
  geom_point()

cor.test(~dist_to_proto_conv5+correct, df2_conv5)
cor.test(~dist_to_proto_conv5+correct, df2_conv5 %>% filter(type == "far distractor"))
cor.test(~dist_to_proto_conv5+correct, df2_conv5 %>% filter(type == "close distractor"))
cor.test(~dist_to_proto_conv5+correct, df2_conv5 %>% filter(type == "target"))
```
